\chapter{Background}
Apart from general text content, structured information is also widely contained by digital document. Among these, many mathematical content (including documents on Internet), are represented markups like \LaTeX\  or MathML, which is in a rich structural way. Retrieval on those information can be challenging but very helpful given the contribution and importance of mathematics to our science.

\section{Difficulties}
Some publications already cover a lot on the difficulties on mathematical content information retrieval, also in respective of the differences between mainstream IR approach with those in math search, and the inadequacy to apply general text search method (e.g. bag of words model) to content in mathematical language.

\section{Related Work}


Math-aware search can b
supplementary
Although mainstream IR research covers exhaustively on general text, information retrieval on structured data will become more and more important 

are gradually 
structured 
? Or have
you gotten stuck in a proof and wanted to know which identities
are applicable so that you can progress?
offer some insight 
Search systems play an essential role in our daily lives because there are
a huge number of pages on the Web. However, we sometimes encounter
problems with how to search for or what to submit as a query when we
want to search for things that cannot be easily expressed in natural language.

Information Retrieval technology has reached maturity, math retrieval is still in
its nascent stages, and many challenges remain. Those challenges are due in part
A math expression is often written in a symbolic language with several lev-
els of abstraction, and often contains rich structural information. Additionally,
notational ambiguities, and syntactical and semantic equivalences, make math
knowledge harder to search.

Search for mathematical expressions is difficult for a number of reasons.
There are numerous representations for expressions, including: L A TEX, (con-
tent and presentatio

As computers appeared, one of the important tasks that emerged was
storing and searching large sets of documents. The inverted index was an
early and natural development in this field. It can be thought of like an index
in a book: it is a structure that maps each term to a list of documents that
contains it. In its most simple form, an inverted index only allows us to find
the documents that contain a given term

More and more math knowledge has become available on the Web, and search
is a gate to such vast treasure of digital mathematics content [11]. Even though
Information Retrieval technology has reached maturity, math retrieval is still in
its nascent stages, and many chal

Unlike general text content, mathematical language, by its nature, has many differences from other textual documents. 

Math information retrieval (MIR) starts to be recognized
as an important very domain-specific sort of information re-
trieval research field.

Mathematical expressions are objects with complex
structures and rather few distinct symbols and terms.

many challenges remain. Those challenges are due in part
to the significant difference of math knowledge from other.
A math expression is often written in a symbolic language with several lev-
els of abstraction, and often contains rich structural information.

\section{Overview}
\subsection{Considerations}
\subsection{Property}
Math-aware search \cite{ddd}

interchangeably 

MathML vs LaTeX

First,
one mathematical formula may use different notations and
thus has different representations. 1 Second, two semanti-
cally different mathematical document can contain the same
number of terms. 2 Also, the order of terms in math language
sometimes matters but can be mutable in other cases, which
implies it is impractical to uniformly apply one single lan-
guage model to mathematical content.

\section{Related Work}

An inverted index is the tool used most commonly in text search. It is
a lookup table from words to the documents that contain them. This idea has
been modified to allow for word locality, phrase searching, index compression,
and distributed indexing. With these and other improvements, systems can
be built to quickly search massive
