\documentclass[]{deedy-resume-openfont}
\begin{document}
\lastupdated

\namesection{Zhong}{Wei}{
\href{mailto:zhongwei@udel.edu}{zhongwei@udel.edu} \\
(302)-561-1226
} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Delaware}
\descript{M.S. in Electrical and Computer Engineering}
\location{August 2015 | Newark, DE, USA \\ 
Cum GPA: 3.867 / 4.0}
\sectionsep

\subsection{Jiliang University (CJLU)}
\descript{B.S. in Information and Computation Science}
\location{2009 $\sim$ 2013 | Hangzhou, P.R. China }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Artificial Intelligence \\
Compiler Design \\
Computer Networks II \\
Embedded System Design \\
Principle of Parallel Comp. Architecture \\
Search and Data Mining \\
Statistical Learning \\
Database System
\sectionsep

\subsection{Undergraduate}
Complex Variables Functions \\
Discrete Mathematics \\
Elementary Algebra \\
Elements of Information Theory \\
Mathematical Analysis \\
Numerical Analysis \\
Ordinary Differential Equation \\
Probability Theory
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skill Set}
\subsection{Programming}
%\location{WEB}
\textbullet{} C/C++ \textbullet{} Shell (Bash) \textbullet{} Python \textbullet{} VHDL \\
\textbullet{} Bison/Flex \textbullet{} SQL \textbullet{} PHP \textbullet{} HTML \textbullet{} R \\
\textbullet{} CSS \textbullet{}  Javasscript/jQuery/AngularJS \\
\sectionsep

\subsection{Softwares}
\textbullet{} MySQL/MariaDB \textbullet{} Bootstrap (CSS \& carousel) \textbullet{} Adobe Flash \textbullet{} jQuery UI \\
\textbullet{} Git \textbullet{} Curl \textbullet{} Redis \textbullet{} Nginx/Apache \\
\textbullet{} Whoosh/CLucene \textbullet{} Jieba \textbullet Wireshark \\
\textbullet{} JIRA \textbullet{} Confluence \textbullet Chef VM server \\

\sectionsep

\subsection{Teamwork}
Agile practice, past working experience \\
in a Scrum management environment. \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
% \custombold{Home}:\href{http://www.eecis.udel.edu/~zhongwei/}{www.eecis.udel.edu/$\sim$zhongwei/} \\
\custombold{Github}:\url{https://github.com/t-k-} \\
% \custombold{Stack Overflow}: -\href{http://stackoverflow.com/users/2736576/wei-zhong}{http://stackoverflow.com/users/2736576}
\custombold{Blog}:\url{http://tkhost.github.io/blog} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Career}
\runsubsection{SevOne}
\descript{| S.M.A.R.T.S program, WEB backend intern}
\descript{(2015 Glassdoor best places to work)}
\location{Jun, 2015 $\sim$ Aug, 2015, Wilmington DE, US }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item PHP/SOAP Unit test, C++/CMake, MySQL development environment.
\item Search engine back-end rewrite using CLucene.
\end{tightemize}
\sectionsep

% \runsubsection{University of Delaware InfoLab}
% \descript{| Researcher}
% \location{2014 $\sim$ 2015, Newark, DE}
% \begin{tightemize}
% \item Research and doing project on information retrieval (IR). 
% \end{tightemize}
% \sectionsep

\runsubsection{Jufeng}
\descript{| Embedded System Developer}
\location{Dec, 2012 $\sim$ Feb, 2013, Hangzhou, P.R. China}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Participation in a P2P library development.
\item Contributed to a visualized trace system for monitoring network traffic.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2011-2012 & Academic Year Research and Innovation \\ 
& Scholarship of Jiliang University. \\
% 2011	     & 3\textsuperscript{rd} Price of Eastern China, The Sixth \\
% & Freescale \texttrademark{} Smart Car Race National Competition.
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    PROJECTS 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\runsubsection{OPMES}
\descript{a mathematical language search engine}
\href{https://github.com/t-k-/opmes}{https://github.com/t-k-/opmes} \\
\vspace{\topsep} % Hacky fix for awkward extra vertical space
My graduate thesis project advised by Prof. Fang Hui. OPMES is a search engine to search math content.
Data structure/algorithms are highly optimized, and OPMES has achieved state-of-the-art efficiency in its research domain.
The demo is now online: \url{http://45.79.133.113/opmes}. 
I also write a paper on OPMES which get accepted by ECIR 2016.
\sectionsep

\runsubsection{Voice Instead}
\descript{a TTS(text to speech) browser extension}
\href{https://chrome.google.com/webstore/detail/voice-instead/kphdioekpiaekpmlkhpaicehepbkccbf}{https://chrome.google.com/webstore}\\
\vspace{\topsep} % Hacky fix for awkward extra vertical space
An extension currently available on {Google Chrome Webstore} with over thousands of users. The extension can convert text to speech and support extremely long content to be read at a time. I use jQuery and jPlayer to build this extension, also include some HTML5 elements.
\sectionsep

% \runsubsection{Form Hero}
% \descript{a form filler browser extension (Beta version)}
% \href{https://chrome.google.com/webstore/detail/form-hero-a-html-form-aut/pelaeciljekjlkaampohnboacfhjobod}{https://chrome.google.com/webstore} \\
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
% Chrome extension that helps user speed their HTML form filling process. Responsive MVC WEB design. AngularJS is heavily used in this project. \\
% \sectionsep

\runsubsection{Smart Keyboard}
\descript{self-learning multitouch keyboard}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
My undergraduate thesis project which uses both BP network and SVM/SMO algorithm to adapt user finger positions. Hardware is based on two GOODIX GT811 5-points touch-screens.
\sectionsep

\runsubsection{tknet}
\descript{a cross-platform P2P library}
\href{https://github.com/t-k-/tknet}{https://github.com/t-k-/tknet} \\
\vspace{\topsep} % Hacky fix for awkward extra vertical space
A P2P network based on traditional centralized-server-based model. Different from other P2P solutions, TKNET are able to use Email server to keep track of center servers. \\
\sectionsep

% \runsubsection{TTL-CPU}
% \descript{A homebrew 8-bit TTL-CPU design}
% \href{https://github.com/t-k-/my-ttl-cpu}{https://github.com/t-k-/my-ttl-cpu} \\
% %\href{http://thoughts-of.me/myttlcpu.pdf}{http://thoughts-of.me/myttlcpu.pdf} \\
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
% I realise the circuit in Multisim. The CPU can run a simple program in 6116 RAM whose initial content is written by a 8052 chip. \\
% \sectionsep

\runsubsection{My Website}
\descript{personal blog and technical notes}
\href{http://tkhost.github.io/blog}{http://tkhost.github.io/blog} \\
%(currently hosted off-line) \\
\vspace{\topsep} % Hacky fix for awkward extra vertical space
An AJAX style blog using vanilla Javascript code written by myself. I use it to write technical notes as a way to inspire my study.
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
